Efficient GPU implementation of multicomponent and multiphase Lattice Boltzmann models.

### 2010-04-04 paper.tex
Add more keywords, heavily update the abstract.

%%%%% Begin Abstract %%%%%%%%%%%
\begin{abstract}
Despite the number and successful implementations of number of lattice Boltzmann systems on Graphics Processing Units (GPUs), the implementation of more complicated problems as multiphase models or Nearest-Neighbours (NN) interaction, which includes all the boundary conditions, on GPUs is still not well developed. The purpose of the paper is twofold: to develop the efficient GPUs implementation algorithms for the binary liquids flows, which are subclass of the NN interactions, and to illustrate the usefullness in terms of performance of GPUs for multiphase models simulations.
\end{abstract}
%%%%% end %%%%%%%%%%%

@@

\ams{52B10, 65D18, 68U05, 68U07{\color{red} We need to find somewhere classifications.}}
\keywords{Lattice Boltzmann method, GPU, Shan-Chen model, Free-energy model, Binary liquids}

>>>>

%%%%% Begin Abstract %%%%%%%%%%%
\begin{abstract}
Graphics Processing Units (GPUs) have been succesfully used to simulate
various systems using the Lattice Boltzmann (LB) method.  The simulations were
usually either a straightforward port of a CPU code (without any
regards to performance considerations), or optimized for single phase
flows.  The implementation of more complicated problems such as
multiphase models or models with Nearest-Neighbours (NN) interaction
has never received any special attention.  The purpose of this paper
is twofold: to illustrate the usefulness of GPUs for multiphase simulations,
and to carefully develop an optimized and efficient algorithm for GPU
simulations of fluid flows using LB models with NN terms.
\end{abstract}
%%%%% end %%%%%%%%%%%

@@

\ams{52B10, 65D18, 68U05, 68U07{\color{red} We need to find somewhere classifications.}}
\keywords{Lattice Boltzmann method, GPU, Shan-Chen model, Free-energy model, binary liquids, multiphase flow, CUDA, OpenCL, GPGPU}
